---
title: "Automated Proximity Analysis EJ with targets"
output:
  html_document:
    theme: spacelab
---


#### David Lopez, Climate Economics Branch


---

## Data Sources


### Community and Health Outcomes:
 - 2021 ACS
 - 2019 AirToxScreen Cancer & Respiratory Illness
 - 2023 CDC PLACES
 
### Facility Geography:
 - LURA All Mills
 - 2020 Toxic Release Inventory
 
 
---

## Automation using `targets`

```{r, message=FALSE, echo=FALSE, warning=FALSE}

library(tidyverse)
library(targets)
library(tarchetypes)
library(kableExtra)


tar_visnetwork(targets_only = TRUE)

```

---

## EJ Proximity Analysis Tables

#### Georgia Pulp/Paper Mills

```{r, message=FALSE, warning=FALSE, echo=FALSE}
GA_ft <- read.csv('GA_paper_mills_finaltable.csv')

GA_ft %>% mutate(across(where(is.numeric), round,2)) %>% 
    kbl(caption = "Overall Community Profile and Health Outcomes for Communities Near Identified Facilities",
        format = "html",
        col.names = c("",
                      "Overall National Average",
                      "Rural Areas National Average",
                      "Within 1 mile of production facility",
                      "Within 3 miles of production facility",
                      "Within 5 miles of production facility",
                      "Within 10 miles of production facility"
        ),
        align = "r") %>%
    kable_styling(bootstrap_options = 'striped') %>% 
    kable_classic(full_width = F, html_font = "Cambria")


```


---

#### National Pellet Mills

```{r, message=FALSE, warning=FALSE, echo=FALSE}
USA_ft <- read.csv('USA_pellet_mills_finaltable.csv') %>% select(2:8)

USA_ft %>% mutate(across(where(is.numeric), round,2)) %>% 
    kbl(caption = "Overall Community Profile and Health Outcomes for Communities Near Identified Facilities",
        format = "html",
        col.names = c("",
                      "Overall National Average",
                      "Rural Areas National Average",
                      "Within 1 mile of production facility",
                      "Within 3 miles of production facility",
                      "Within 5 miles of production facility",
                      "Within 10 miles of production facility"
        ),
        align = "r") %>%
    kable_styling(bootstrap_options = 'striped') %>% 
    kable_classic(full_width = F, html_font = "Cambria")


```


#### Louisiana All TRI Facilities


```{r, message=FALSE, warning=FALSE, echo=FALSE}
LA_ft <- read.csv('LA_all_tri_finaltable.csv') %>% select(2:8)

LA_ft %>% mutate(across(where(is.numeric), round,2)) %>% 
    kbl(caption = "Overall Community Profile and Health Outcomes for Communities Near Identified Facilities",
        format = "html",
        col.names = c("",
                      "Overall National Average",
                      "Rural Areas National Average",
                      "Within 1 mile of production facility",
                      "Within 3 miles of production facility",
                      "Within 5 miles of production facility",
                      "Within 10 miles of production facility"
        ),
        align = "r") %>%
    kable_styling(bootstrap_options = 'striped') %>% 
    kable_classic(full_width = F, html_font = "Cambria")


```



---

## Next Steps..

 - Facility Profile Tables.
 - Update datasets.
 - Explore further outcomes and facilities.








